\documentclass[11pt]{article}
% ============================================================================
% Supplement to the JASA-structured MWQTM manuscript.
%   A. Proofs            (transport/identification/orthogonality/remainder/
%                         one-step normality/sandwich; clustered Bahadur;
%                         censoring orthogonality)  -- imported proof bodies
%   B. Algorithms and implementation
%   C. Additional simulations (audit and sensitivity tables)
%   D. Additional application details
% ============================================================================
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,bm,booktabs,graphicx,natbib,hyperref}
\usepackage{xr}
\externaldocument{paper}                      % cross-reference the main paper
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{condition}{Condition}
\theoremstyle{remark}\newtheorem{remark}{Remark}
\newcommand{\E}{\mathbb{E}}
\newcommand{\PR}{\mathbb{P}}
\newcommand{\Pn}{\mathbb{P}_n}
\newcommand{\Gn}{\mathbb{G}_n}
\newcommand{\X}{\bm{X}}
\newcommand{\Z}{\bm{Z}}
\newcommand{\bbeta}{\bm{\beta}}
\newcommand{\bgamma}{\bm{\gamma}}
\newcommand{\bth}{\bm{\theta}}
\newcommand{\indc}[1]{\mathbf{1}\{#1\}}
\newcommand{\given}{\,\vert\,}
\newcommand{\binit}{\widehat\bbeta_{\rm init}}
\newcommand{\rom}{r_{\omega}}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\theequation}{S\arabic{equation}}

\title{\bf Supplement to ``Event-aligned conditional quantile trajectories of a
biomarker before disease onset under left truncation and competing death''}
\author{\thanks{}}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\bigskip

This supplement collects the proofs (Section~\ref{supp:proofs}), the estimation
algorithms and implementation details (Section~\ref{supp:algo}), the full set of
simulation and audit/sensitivity studies summarized in Section~\ref{sec:sim} of the
main paper (Section~\ref{supp:sims}), and additional details of the application
(Section~\ref{supp:app}). Equations, tables, and figures are numbered S1, S2, \dots;
references of the form ``Theorem~1'' point to the main paper.

% ============================================================================
\section{Proofs}\label{supp:proofs}
This section reproduces the asymptotic theory: the transport/identification
arguments, the implicit density-weighted orthogonalization, the censoring
orthogonality ($\chi^C=0$), the sharper-remainder bound, the high-level
cross-fitted one-step asymptotic normality and sandwich consistency, and the
clustered, weighted, growing-sieve Gram/Knight/Bahadur representation that verifies
the high-level conditions for the concrete sieve. The numbering of internal
results is self-contained within this section.

\subsection*{S1.A\quad Identification, orthogonality, one-step normality, sandwich}
\input{proof_body}

\subsection*{S1.B\quad Censoring orthogonality of the IPW quantile score}
\input{censoring_orthogonality_body}

\subsection*{S1.C\quad Clustered weighted growing-sieve Bahadur representation}
\input{bahadur_body}

% ============================================================================
\section{Algorithms and implementation}\label{supp:algo}

\paragraph{Sieve basis.} The baseline surface $m_{\tau}(u,t)$ uses a tensor-product
cubic B-spline basis $\{B_k(u,t)\}$ over the two time scales, a partition of unity
(so no separate intercept enters the design). The implementation uses this
partition-of-unity basis; the asymptotic analysis (Section~\ref{supp:proofs}) uses
the $L_2$-normalized basis $\widetilde B_k=\sqrt K\,B_k$, under which the population
Gram has eigenvalues bounded away from $0$ and $\infty$; the two differ by the
fixed scaling $\sqrt K$, which cancels in the estimator.

\paragraph{Complexity selection (A-CV).} The number of interior knots / spline
degrees of freedom and any penalty $\lambda_n$ are chosen by subject-level
$K$-fold cross-validation minimizing the held-out check loss (the ``-CV'' suffix).
A fixed richer-sieve fit (``A-Rich'', $K{+}2$) is reported as a sensitivity
comparison, not a theory-guided undersmoothing rule. The reported pilot uses a
regression-spline sieve (fixed knots, $\lambda_n=0$).

\paragraph{Sparsity and projection (B-OS-CF).} The conditional density at the
quantile, $f_\tau(0)$, is estimated by the Hendricks--Koenker quantile-spacing
sparsity $\widehat f_\tau(0)=\{(\widehat q_{\tau+a_n}-\widehat q_{\tau-a_n})/(2a_n)\}^{-1}$,
rearranged for positivity and truncated to $[f_{\min},f_{\max}]$. The
density-weighted projection $\widehat g_{\tau,\omega}$ solves a weighted spline
least-squares regression of $\X$ on $B_g(u,t)$ with weights
$a_\omega\widehat f_\tau(0)$. Cross-fitting over subject folds is part of the
estimator definition (Section~\ref{sec:onestep} of the main paper).

\paragraph{Bootstrap and fold discipline.} Inference for the A-CV point estimator
uses a full-pipeline subject-level bootstrap: subjects (not observations) are
resampled, preserving within-subject clustering, and the entire pipeline
(complexity selection and, for B-OS-CF, nuisance fitting) is refit on each
resample. Cross-validation folds are formed by subject id, so no subject's visits
appear in both training and held-out folds; a controlled same-dataset comparison
(Table~\ref{tab:leakfold}) quantifies the effect of violating this fold discipline.

\paragraph{Crossing.} Predicted quantile curves are made monotone in $\tau$ by
rearrangement; this is a pointwise post-processing step that does not alter the raw
$\widehat\bbeta_\tau$ used for inference.

\paragraph{Reproducibility and computational audit.} A computational-failure audit
(Table~\ref{tab:audit}) records the disposition of every replicate (QR-solver
status, degenerate folds, support-mask exclusions) so that reported summaries are
not silently conditioned on ``clean'' replicates. Code is available at the
companion repository.

% ============================================================================
\section{Additional simulations}\label{supp:sims}
This section gives the full designs and complete tables for the studies summarized
in Section~\ref{sec:sim} of the main paper. Unless noted, $R$ denotes the number of
Monte-Carlo replicates and coverage is for the $95\%$ subject-bootstrap interval.

\subsection{Estimator family and finite-sample inference}
\input{table_estimators}
\input{table_estfull}
\input{table_estse}
\input{table_bosc}

\subsection{Censoring weights and orthogonality}
The complete-event (CC), IPCW, and oracle-weight (ORC) estimators, the
estimated-vs-oracle weight-gap rate, and hard-censoring behavior.
\input{table_cc}
\input{table_compare}
\input{table_censhard}
\input{table_corr}

\subsection{Surface recovery and density-weighted centering}
\input{table_surface}
\input{table_ordcenter}
\input{table_studentized}

\subsection{Sieve growth, tuning, and cross-validation behavior}
\input{table_sieve}
\input{table_sievetail}
\input{table_tuning}
\input{table_ladder}
\input{table_cvfreq}
\input{table_fixedj}

\subsection{Fold discipline and randomization}
\input{table_foldsens}
\input{table_leakfold}

\subsection{Non-Gaussian errors and crossing}
\input{table_dist}
\input{table_sievedist}
\input{table_crossing}

\subsection{Onset-distribution robustness (non-proportional hazards / AFT) and pilot}
\input{table1}
\input{table_nonph}

\subsection{Computational reproducibility audit}
\input{table_audit}

\subsection{Comparison with the conditional-mean estimator of Sun et al.}
\label{supp:sun}
Full numbers for the five-regime comparison of Section~\ref{sec:suncmp}.
Table~\ref{tab:cmp-beta} reports distributional-effect recovery and scalar-slope
variability (with the oracle-$\alpha$ decomposition discussed in the main text);
Table~\ref{tab:cmp-contrast} the mean-contrast IMSE for Sun-basic, the stratified
Sun-S extension, and the two quantile reconstructions Q-LN and Q-INT, with paired
Monte-Carlo standard errors; Table~\ref{tab:cmp-surface} the conditional-mean
surface and Sun bandwidth sensitivity; and Table~\ref{tab:cmp-heavy} the
heavy-tail (DGP5) robustness diagnostics.
\input{table_compare2}

% ============================================================================
\section{Additional application details}\label{supp:app}

\paragraph{Synthetic cohort.} The illustrative analysis of Section~\ref{sec:app}
uses a synthetic cohort generated to match the ADNI sampling design: covariates are
a binary \emph{APOE4} carrier indicator and sex; onset (amyloid positivity) is
Cox--Weibull; competing death is Weibull; entry is staggered with left truncation;
loss to follow-up is independent given $(A,\X)$; visits are noninformative. The
log-marker is generated with a covariate effect that varies across quantile levels
so that the carrier effect $\beta_{\tau,1}$ is non-flat in $\tau$, illustrating a
distributional (not pure-location) effect. \emph{These are not real ADNI data and
the figures are for illustration of the deliverables only; the substantive ADNI
analysis is in preparation.}

\paragraph{Estimable region and masks.} Quantile surfaces are reported on the
interior region where the visit occupation density is bounded away from zero; grid
cells with fewer than a minimum number of nearby complete-event visits are masked.

\paragraph{Sensitivity.} For the real-data analysis we will report sensitivity to
(i) the weighting (CC default vs.\ IPCW design-standardization), (ii) the
inferential route (A-CV with subject bootstrap vs.\ B-OS-CF), and (iii) crossing
(rearrangement of predicted curves), following the same protocol validated in
Section~\ref{supp:sims}.

\end{document}
